\section{Existing Games}

As IRLVRMMOs are a relatively new genre of games, there are only a limited amount of commonly known games on the market. This makes it somewhat hard to compare how others of such games work under the hood, but gives a whole new area to experiment with and make very unique games, or mimics of existing pc games.

In this section we will look into 2 larger IRLVRMMOs and what challenges and tasks they throw at the players.


\subsection{Niantic Project Ingress}

The Niantic Project, better known as Ingress, is one of the first and more commonly known IRLVRMMOs\cite{ingress:submissions}. It is developed by nianticlabs at google and released for Android devices, where players capture regions generated from Google Maps by using the mobile application. The game uses Google Maps to get an in-game representation of any area the player may be playing in. It uses Historical Markers\cite{ingress:maps} as well as community feedback, to generate ingame content such as the location of control points called portals.

The players' objectives is to hack Portals to take them over, and triangulate between portals, as this creates "Mind Units" which is the enemy team's players that will be unable to regain  the area for some time. 
%Ingress is also a game of strategy and both cooperative and competitive, as you sometimes will need a group of players to hack larger portals, and will need to lock off the enemy team for regaining the portals.


\subsection{Megabits}

Another game is Megabits\cite{megabits}, which is developed for iPhone by a small indie game company. Megabits is a virtual pet training and dueling game, which takes place in the real world. Just as Ingress, Megabits uses Google Maps and places the Megabit monsters at predefined locations, that the players can visit to catch the megabits. Megabit is based on the Pokémon games, and is very equivalent to this with the exception that it takes place in the real world.

%Megabits mainly seems to focus on competitive play, as the only user to user action is the duels between them. The rest of the game can be played alone as you can catch and train your megabits by yourself. This may lead to the question if this game truly is a Massive Multiplayer Online, or just a Multiplayer game.